Learning Causally-Generated Stationary Time Series

### 2017-02-23 doc/paper.tex
Minor edit

\begin{document}
\twocolumn[
    \icmltitle{Learning Causally-Generated Stationary Time Series}
    \icmlsetsymbol{equal}{*}
    \begin{icmlauthorlist}
    \icmlauthor{Wessel P.\ Bruinsma}{invenia}
    \icmlauthor{Rich E.\ Turner}{cam}
    \end{icmlauthorlist}
    \icmlaffiliation{cam}{University of Cambridge, Cambridge, United Kingdom}
    \icmlaffiliation{invenia}{Invenia Labs Limited, Cambridge, United Kingdom}
    \icmlcorrespondingauthor{Wessel Bruinsma}{wessel.bruinsma@invenialabs.co.uk}
    \icmlkeywords{ICML, machine learning, probabilistic modelling, approximate inference, Gaussian process, causality}
    \vskip 0.3in
]
\printAffiliationsAndNotice{}
% \printAffiliationsAndNotice{\icmlEqualContribution}
% \footnotetext{hi}

@@

\section{Introduction}
Classically, nature is considered to be \textit{causal}, meaning that at any point in time the output of any realisable system can only depend on past values of the input. We should aim to include this inductive bias---\textit{causality}---in modelling dynamical phenomena, since that would exclude any unrealisable system from the model prior.

>>>>

\begin{document}
\twocolumn[
    \icmltitle{Learning Causally-Generated Stationary Time Series}
    \icmlsetsymbol{equal}{*}
    \begin{icmlauthorlist}
    \icmlauthor{Wessel P.\ Bruinsma}{invenia}
    \icmlauthor{Richard E.\ Turner}{cam}
    \end{icmlauthorlist}
    \icmlaffiliation{cam}{University of Cambridge, Cambridge, United Kingdom}
    \icmlaffiliation{invenia}{Invenia Labs Limited, Cambridge, United Kingdom}
    \icmlcorrespondingauthor{Wessel Bruinsma}{wessel.bruinsma@invenialabs.co.uk}
    \icmlkeywords{ICML, machine learning, probabilistic modelling, approximate inference, Gaussian process, causality}
    \vskip 0.3in
]
\printAffiliationsAndNotice{}
% \printAffiliationsAndNotice{\icmlEqualContribution}
% \footnotetext{hi}

@@

\section{Introduction}
Many natural phenomena are \textit{causal} meaning that at any point in time the output of any realisable system can only depend on past values of the input. We should aim to include this inductive bias---\textit{causality}---in modelling dynamical phenomena, since that would exclude any unrealisable system from the model prior.
